### 2024-01-20 tex/ack.tex
[ update ] acknowledgements

Special thanks go to Guillaume Allais, Jan de Muijnck-Hughes, and James McKinna,
all of whom have read all or part of this thesis in draft form and whose
comments have lead to great improvements in the final document.
Similar thanks go to the anonymous reviewers of the papers that have lead to and
formed part of this thesis.

@@

I thank my family, particularly for our time together in the COVID-19
lockdown/work-from-home period.
The pandemic caused difficulties for us all, but a positive approach got us
through it and let us take advantage of what we could.
More recently, I thank Ayaka, who has listened to and supported me over the last
year of write-up.
Above all, she has been very patient, and with my thesis-writing now ending, I
hope that we can live our lives more fully together.

>>>>

Special thanks go to Guillaume Allais, Jan de Muijnck-Hughes, and James McKinna,
all of whom have read all or part of this thesis in draft form and whose
comments have lead to great improvements in the final document.
Similar thanks go to the anonymous reviewers of the papers that have lead to and
formed part of this thesis.
More recently, I also thank my examiners Kathrin Stark and Conor McBride,
whose keen and careful reading have lead to yet more improvements to this final
version of my thesis.

@@

I thank my family, particularly for our time together in the COVID-19
lockdown/work-from-home period.
The pandemic caused difficulties for us all, but a positive approach got us
through it and let us take advantage of what we could.
More recently, I thank Ayaka, who has listened to and supported me over the last
year of write-up.
Alas, the writing process can take a toll on relationships, so I wish her all
the best.
